%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Assistant Director, Data Scientist} % Job title
    {Moody's Analytics} % Organization
    {Remote/Heredia, Costa Rica} % Location
    {Jun. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Currently Leading QA and RAG development for a client-facing LLM-powered application.}
        \item {Developed }
        \item {Research and Development for a climate-adjusted default probability model.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Professional Statistical Analyst} % Job title
    {Fiserv (Now Infinite Computer Solutions)} % Organization
    {Remote/San José, Costa Rica} % Location
    {Sep. 2021 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Advanced analytics consulting, including designing, developing, and deploying machine learning solutions.}
        \item {Contact: Freddy Guzmán - freddy.guzman@infinite.com}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Hydroclimate Junior Data Scientist/Engineer} % Job title
    {Instituto Costarricense de Electricidad (ICE)} % Organization
    {San José, Costa Rica} % Location
    {Nov. 2018 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Statistical analysis and prediction of hydroclimate phenomena, quantitative risk assessment, and infrastructure portfolio optimization.}
        \item {Contact: Berny Fallas - BeFall@ice.go.cr; +(506) 8842-3304}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Infrastructure Design Engineer} % Job title
    {DEHC Ingenieros Consultores} % Organization
    {San José, Costa Rica} % Location
    {Apr. 2016 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Civil infrastructure consulting for land development, hydrologic statistical, and computational modeling.}
        \item {Contact: Alejandro Chacón - alechaconv@joturus.com; +(506) 8703-3466}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}