%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Evaluation framework for GenAI application} % Project name
    {Lead} % Role
    {Moody's Analytics} % Organization
    {Feb. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Led a squad of 2 people to design and develop the QA framework for the central client-facing GenAI application within 3 months.}
        \item {Tech: LangSmith, LangChain, OpenAI}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Price Sensitivity Analysis for US Merchant Portfolio} % Project name
    {Lead} % Role
    {Fiserv (Now Infinite Computer Solutions)} % Organization
    {May. 2022 - May. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Led a team of 3 to assist in business decisions affecting over 100K US clients, with an expected revenue increase of over \$30M.}
        \item {Performed advanced analytics and pricing strategy modeling.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Recommender System POC for Banking Card Platform} % Project name
    {Developer} % Role
    {Fiserv (Now Infinite Computer Solutions)} % Organization
    {Feb. 2022 - Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed a proof of concept for a recommender system as part of a Global Incubator Challenge.}
        \item {Now being taken into production by a development team, expected to impact over 1 million cardholders.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Google AI \& ICE Flood Forecasting System} % Project name
    {Co-Promoter} % Role
    {Instituto Costarricense de Electricidad (ICE)} % Organization
    {Sep. 2020 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Pioneered a flood forecasting system in Central America with potential life-saving applications and economic impact reduction during tropical storms.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Energy Infrastructure Time Series Simulation Model} % Project name
    {Co-Promoter} % Role
    {Instituto Costarricense de Electricidad (ICE)} % Organization
    {Oct. 2020 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed a simulation model to improve decision-making and the robustness of ROI estimations for energy infrastructure projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Big Data Project for Mobility Pattern Segmentation} % Project name
    {Co-Promoter} % Role
    {Instituto Costarricense de Electricidad (ICE)} % Organization
    {Mar. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Analyzed over 8 billion rows of data to enhance decision-making for key government stakeholders during the COVID-19 pandemic.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}