%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MicroMasters in Statistics and Data Science} % Degree
    {MITx} % Institution
    {Online} % Location
    {Aug. 2020 - May. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Capstone Exam}
        \item{Data Analysis: Statistical Modeling and Computation in Applications}
        \item{ML with Python-From Linear Models to Deep Learning}
        \item{Fundamentals of Statistics}
        \item{Probability - The Science of Uncertainty and Data}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {MSc. in Hydraulic Engineering} % Degree
    {Universidad de Costa Rica} % Institution
    {San José, Costa Rica} % Location
    {Mar. 2017 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{\textit{Suma Cum Laude}}
        \item {Thesis (with distinction): A copula analysis was used to assess the risk of flooding in the largest river system of Costa Rica.}
        \item {1st in class in Stochastic Hydrology.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lic. in Civil Engineering} % Degree
    {Universidad de Costa Rica} % Institution
    {San José, Costa Rica} % Location
    {Mar. 2009 - Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{\textit{Top 10 out of 30k applications}}
        \item {Thesis (with distinction): A methodology for prioritization of investment in culverts was created based on risk profiling.}
        \item {High academic performance in Programming Principles (9/10), Intro to Probability and Statistics (9.5/10), and Systems Engineering (9.5/10).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}