%---------------------------------------------------------
%	SECTION TITLE
%---------------------------------------------------------
\cvsection{Work Experience}

%---------------------------------------------------------
%	CONTENT
%---------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Assistant Director, Data Scientist} % Job title
    {Moody's Analytics} % Organization
    {Heredia, Costa Rica, hybrid} % Location
    {Jun. 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Responsibilities:} Research and development for model enhancement and quality assurance mechanisms for client facing products.}
        \item {\textbf{Key Projects:}}
        \item {\textit{Evaluation Framework for GenAI Application} - Led the design and development of a QA framework for a client-facing GenAI application, delivering a working prototype in less than 3 months.}
        \item{\textit{GenAI for Client Support} - Developed from scratch the RAG system of an application to help model SME identify useful sources of information of answer client methodological questions.}
        \item {\textit{Climate Adjusted PD Improvements} - Proposed enhancements to the current methodology, increasing model consistency by more than 20\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Professional Statistical Analyst} % Job title
    {Fiserv/Infinite Computer Solutions} % Organization
    {San José, Costa Rica, hybrid} % Location
    {Sep. 2021 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Responsibilities:} Advanced analytics consulting, design, development, and deployment of machine learning solutions.}
        \item {\textbf{Key Projects:}}
        \item {\textit{Advanced Analytics Marketing Roadmap for Point of Sales Organization} - Designed a 2-year advanced analytics roadmap tailored to the marketing department’s needs. Led a team of three to deliver 3 MVPs addressing key priorities within 2 months.}
        \item {\textit{Price Sensitivity Analysis for US Merchant Portfolio} - Led a team of three, conducting a price sensitivity analysis that influenced business decisions affecting over 100,000 clients. Recommended changes were expected to generate\$ 30M in additional revenue.}
        \item {\textit{Recommender-System Proof of Concept} - Developed a recommender-system using multimodal data for a banking card platform of over 1 million cardholders.}
        \item {\textit{Ticket Past Due Prediction} - Developed an Early Warning Signal system for tickets for the Risk Management Organization.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Hydroclimate Junior Data Scientist} % Job title
    {Instituto Costarricense de Electricidad (ICE)} % Organization
    {San José, Costa Rica} % Location
    {Nov. 2018 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Responsibilities:} Statistical analysis and prediction of hydro-climate phenomena, risk assessments, and infrastructure portfolio optimization.}
        \item {\textbf{Key Projects:}}
        \item {\textit{Google AI and ICE Flood Forecasting System} - Promoted the partnership between the organizations to implement a flood forecasting system using AI, a pioneer project in Central America with the potential to save lives during tropical storms.}
        \item {\textit{Time Series Simulation Model for Energy Infrastructure} - Co-promoted and developed a time series simulation model, improving the robustness of ROI estimation for energy projects.}
        \item {\textit{Machine Learning Erosion Prediction} Promoted and developed novel methodology to predict erosion in reservoir cleaning maneuvers.}
        \item {\textit{Mobility Pattern Segmentation}: Co-promoted and co-developed a model to capture mobility patterns using telecommunications data. More than 8 Billion rows analyzed}
        \item {\textit{River system sediment analytics} Managed data sampling and automated the sedimentological analysis reporting of erosion patterns in the lower basin of the Reventazón river system.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Infrastructure Design Engineer} % Job title
    {DEHC Ingenieros Consultores} % Organization
    {San José, Costa Rica} % Location
    {Apr. 2016 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Responsibilities:} water infrastructure design consulting,  including hydrologic statistical modeling and computational design for land development.}
        \item {\textbf{Key Projects:}}
        \item {\textit{Bridge and Culvert Design} - Led a team of 3 Engineers in the hydrological and hydraulic analysis and design of more than 20 bridges and 150 culverts for key national highway.}
        \item{\textit{Stormwater Management Design} - Helped in the analysis and redesign of a mayor storm water system in San José City}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}